Graph-Based Neural Reconstruction \\ from Skeletonized 3D Networks

### 2017-11-15 papers/cvpr2018/3_evaluation.tex
added HP evaluation and results

We evaluate our method on two connectomics datasets and compare it to a state-of-the-art pixel-based reconstruction method using the variation of information (VI) metric.
\hp{depending on space we can shorten this and put details into the supplemental material}

@@

We use the following two datasets for training and experimental evaluation.

\paragraph{Kasthuri.}
The Kasthuri dataset consists of scanning electron microscope images of the neocortex of a mouse brain~\cite{kasthuri2015saturated}. This dataset is $5342 \times 3618 \times 338$ voxels in size. The resolution of the dataset is $\SI[product-units=single]{3 x 3 x 30}{\nano\meter}^3$ per voxel. We evaluate our methods using the left cylinder of this 3-cylinder dataset. We downsample the dataset in the $x$ and $y$ dimensions to give a final resolution of $\SI[product-units=single]{6 x 6 x 30}{\nano\meter}^3$ per voxel. We divide the dataset into two volumes (Vol. 1 and Vol. 2) along the $x$ dimension where each volume is $\SI[product-units=single]{8.0 x 10.9 x 10.1}{\micro\meter}^3$.

\paragraph{FlyEM.}
The FlyEM dataset comes from the mushroom body of a 5-day old adult male Drosophila fly imaged by a focused ion-beam milling scanning electron microscopy~\cite{takemura2017connectome}. The mushroom body in this species is the major site of associative learning. The original dataset contains a $\SI[product-units=single]{40 x 50 x 120}{\micro\meter}^3$ volume of which we use two cubes of size $\SI[product-units=single]{10 x 10 x 10}{\micro\meter}^3$. The resolution of this dataset is $\SI[product-units=single]{10 x 10 x 10}{\nano\meter}^3$ or $1000$ voxels in each dimension in each of the two volumes.

@@

The segmentation on the Kasthuri dataset was computed by agglomerating 3D supervoxels produced by the z-watershed algorithm from 3D affinity predictions~\cite{zlateski2015image}. A recent study by Funke et al.~\cite{schlegel2017learning} demonstrated superior performance of such methods over existing ones on anisotropic data. We learn 3D affinities using MALIS loss with a U-net~\cite{Turaga:2009,ronneberger2015u}. We apply the z-watershed algorithm with suitable parameters to compute a 3D oversegmentation of the volume. The resulting 3D oversegmentation is then agglomerated using the technique of context-aware delayed agglomeration to generate the final segmentation~\cite{10.1371/journal.pone.0125825}. We use this segmentation as our baseline for comparisons with our method.

For the FlyEM data we collected two $1000 \times 1000 \times 1000$ voxel ($\SI[product-units=single]{10x10x10}{\micro\meter}^3$) volumes from the authors~\cite{takemura2017connectome}. Based on the authors' suggestion, we applied a context-aware delayed agglomeration algorithm~\cite{10.1371/journal.pone.0125825} that shows improved performance on this dataset over the pipeline used in the original publication. This segmentation framework learns voxel and supervoxel classifiers with an emphasis to minimize under-segmentation error. At the same time this framework produces lower oversegmentation than standard algorithms. The algorithm first computes multi-channel 3-D predictions for membranes, cell interiors, and mitochondria, among other cell features. The membrane prediction channel is used to produce an over-segmented volume using 3D watershed, which is then agglomerated hierarchically up to a certain confidence threshold. We used exactly the same parameters as the publicly available code for this algorithm.

>>>>

We evaluate our method by comparing it to a state-of-the-art pixel-based reconstruction approach using datasets from two different animals.

@@

\paragraph{Kasthuri.}
The Kasthuri dataset consists of scanning electron microscope images of the neocortex of a mouse brain~\cite{kasthuri2015saturated}. This dataset is $5342 \times 3618 \times 338$ voxels in size. The resolution of the dataset is $\SI[product-units=single]{3 x 3 x 30}{\nano\meter}^3$ per voxel. We evaluate our methods using the left cylinder of this 3-cylinder dataset. We downsample the dataset in the $x$ and $y$ dimensions to give a final resolution of $\SI[product-units=single]{6 x 6 x 30}{\nano\meter}^3$ per voxel. We divide the dataset into two volumes (Vol. 1 and Vol. 2) along the $x$ dimension, where each volume is $\SI[product-units=single]{8.0 x 10.9 x 10.1}{\micro\meter}^3$ or $X \times Y \times Z$ voxels. \hp{add voxels}

\paragraph{FlyEM.}
The FlyEM dataset comes from the mushroom body of a 5-day old adult male Drosophila fly imaged by a focused ion-beam milling scanning electron microscopy~\cite{takemura2017connectome}. The mushroom body in this species is the major site of associative learning. The original dataset contains a $\SI[product-units=single]{40 x 50 x 120}{\micro\meter}^3$ volume with a resolution of $\SI[product-units=single]{10 x 10 x 10}{\nano\meter}^3$ per voxel. We use two cubes (Vol. 1 and Vol. 2) of size $\SI[product-units=single]{10 x 10 x 10}{\micro\meter}^3$ or $1000 \times 1000 \times 1000$ voxels.

@@

The segmentation on the Kasthuri dataset was computed by agglomerating 3D supervoxels produced by the z-watershed algorithm from 3D affinity predictions~\cite{zlateski2015image}. A recent study by Funke et al.~\cite{schlegel2017learning} demonstrated superior performance of such methods over existing ones on anisotropic data. We learn 3D affinities using MALIS loss with a U-net~\cite{Turaga:2009,ronneberger2015u}. We apply the z-watershed algorithm with suitable parameters to compute a 3D oversegmentation of the volume. The resulting 3D oversegmentation is then agglomerated using the technique of context-aware delayed agglomeration to generate the final segmentation~\cite{10.1371/journal.pone.0125825}. We use results from this NeuroProof algorithm as the baseline for our comparisons.

For the FlyEM data, based on the authors' suggestion~\cite{takemura2017connectome}, we applied a context-aware delayed agglomeration algorithm~\cite{10.1371/journal.pone.0125825} that shows improved performance on this dataset over the pipeline used in the original publication. This segmentation framework learns voxel and supervoxel classifiers with an emphasis to minimize under-segmentation error. At the same time this framework produces lower over-segmentation than standard algorithms. The algorithm first computes multi-channel 3-D predictions for membranes, cell interiors, and mitochondria, among other cell features. The membrane prediction channel is used to produce an over-segmented volume using 3D watershed, which is then agglomerated hierarchically up to a certain confidence threshold. We used exactly the same parameters as the publicly available code for this algorithm.
